Quantum assisted unsupervised data clustering on the basis of neural networks

### 2020-04-22 manuscript.tex
fixed bug in last sentence of third paragraph section 2A
Fix style: one line one sentence

Now for this demonstration let us assume we have $k$ input vectors and $l$ cluster states. The $i$th input vector and $j$th cluster vector are respectively denoted as $\left| x_i \right\rangle$ ($\left| y_j \right\rangle$.

@@

The next stage, for each pair $\{X\}$ and $\{Y\}$, an accumulated information of all the differences is projected into the amplitude of the superposed state. this is achieved by applying the Hadamard gate on auxiliary qubit, then control phase gate on $\left| Xa \right\rangle$,

@@

\begin{equation}
    \left| \psi_2 \right\rangle = H_a\left| \psi_1 \right\rangle = 
    \sum\limits_{i, j}^{k} 
    \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
    \left| y^1_j, \dots, y^n_j \right\rangle
    \dfrac{\left| 0 \right\rangle + \left| 1 \right\rangle}{\sqrt{2}}
\end{equation}

@@

\begin{multline}
    \left| \psi_3 \right\rangle = R_{(X,a)}\left(\dfrac{\pi}{n}\right)\left| \psi_2 \right\rangle
    \\ = \dfrac{1}{\sqrt{2}}
				\sum\limits_{i, j}^{k} 
				\left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 0 \right\rangle
        \\ + \dfrac{1}{\sqrt{2}}
				\sum\limits_{i, j}^{k}
        \exp\left(\dfrac{-i \pi}{n}\sum\limits_l^n d^l_{ij} \right)
        \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 1 \right\rangle
\end{multline}

%\\ = \dfrac{1}{\sqrt{2}}
%    \sum\limits_{i, j}^{k}
%    \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
%        \left| y^1_j, \dots, y^n_j \right\rangle 
%        \left| 0 \right\rangle
%        \\ + \dfrac{1}{\sqrt{2}}
%				\sum\limits_{i, j}^{k}
%        \left| R(d^1_{ij}, 1)\left(\dfrac{\pi}{n}\right), \dots, R(d^n_{ij}, 1)\left(\dfrac{\pi}{n}\right) \right\rangle 
%        \left| y^1_j, \dots, y^n_j \right\rangle 
%        \left| 1 \right\rangle

@@

\begin{multline}
    \left| \psi_4 \right\rangle = 
    \sum\limits_{i, j}^{k} 
    e^{\left(\dfrac{-i \pi}{2n}\sum\limits_l^n d^l_{ij} \right)}
		\\ \times
        \left\{\cos\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+ 
        \left. i \sin\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 1 \right\rangle\right\}
\end{multline}

@@

\begin{multline}
    \left| \psi_f \right\rangle = 
    \mathrm{CNOT(Y,X)\left| \psi_4 \right\rangle} \\=  
    \sum\limits_{i, j}^{k} 
    e^{\left(\dfrac{-i \pi}{2n}\sum\limits_l^n d^l_{ij} \right)}
				\left\{\cos\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| X_i \right\rangle 
        \left| Y_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+
        \left. i \sin\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| X_i \right\rangle 
        \left| Y_j \right\rangle 
        \left| 1 \right\rangle\right\}
\end{multline}

@@

% Please , add comparison of complexities in number of gates for realization between our scheme and previously proposed schemes (one qubit and two qubit separately)  
% ??

%\begin{align}
%\\
%\end{align} 
%

%
%\begin{equation}
%\end{equation}
%(a black region indicates if the word occurs in the abstract)

>>>>

Now for this demonstration let us assume we have $k$ input vectors and $l$ cluster states. 
The $i$th input vector and $j$th cluster vector are respectively denoted as $\left| x_i \right\rangle$ and $\left| y_j \right\rangle$.

@@

The next stage, for each pair $\{X\}$ and $\{Y\}$, an accumulated information of all the differences is projected into the amplitude of the superposed state. 
This is achieved by applying the Hadamard gate on auxiliary qubit, then control phase gate on $\left| Xa \right\rangle$,

@@

\begin{equation}
    \left| \psi_2 \right\rangle = H_a\left| \psi_1 \right\rangle = 
    \frac{1}{\sqrt{kl}} \sum\limits_{i, j}^{k} 
    \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
    \left| y^1_j, \dots, y^n_j \right\rangle
    \dfrac{\left| 0 \right\rangle + \left| 1 \right\rangle}{\sqrt{2}}
\end{equation}

@@

\begin{multline}
    \left| \psi_3 \right\rangle = R_{(X,a)}\left(\dfrac{\pi}{n}\right)\left| \psi_2 \right\rangle
    \\ = \dfrac{1}{\sqrt{2kl}}
				\sum\limits_{i, j}^{k} 
				\left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 0 \right\rangle
        \\ + \dfrac{1}{\sqrt{2kl}}
				\sum\limits_{i, j}^{k}
        \exp\left(\dfrac{-i \pi}{n}\sum\limits_l^n d^l_{ij} \right)
        \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 1 \right\rangle
\end{multline}

@@

\begin{multline}
    \left| \psi_4 \right\rangle = 
    \frac{1}{\sqrt{kl}} \sum\limits_{i, j}^{k} 
    e^{\left(\dfrac{-i \pi}{2n}\sum\limits_l^n d^l_{ij} \right)}
		\\ \times
        \left\{\cos\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+ 
        \left. i \sin\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| d^1_{ij}, \dots, d^n_{ij} \right\rangle 
        \left| y^1_j, \dots, y^n_j \right\rangle 
        \left| 1 \right\rangle\right\}
\end{multline}

@@

\begin{multline}
    \left| \psi_f \right\rangle = 
    \mathrm{CNOT(Y,X)\left| \psi_4 \right\rangle} \\=  
    \frac{1}{\sqrt{kl}}\sum\limits_{i, j}^{k} 
    e^{\left(\dfrac{-i \pi}{2n}\sum\limits_l^n d^l_{ij} \right)}
				\left\{\cos\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| X_i \right\rangle 
        \left| Y_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+
        \left. i \sin\left(\dfrac{\pi}{2n}\sum\limits_l^n d^l_{ij} \right)
        \left| X_i \right\rangle 
        \left| Y_j \right\rangle 
        \left| 1 \right\rangle\right\}
\end{multline}

@@
